\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Cristian Rubén Recabarren Madrid}
\date{}
\begin{document}
\maketitle

\section*{Contact Information}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Phone: +56 9 9834 7770
  \item Email: crecabar\_cl@me.com
\end{itemize}

\section*{Profile}
Bachelor of Engineering Science in Computer Science with a strong background in software development and a proven track record in leading and managing teams for successful project delivery. Committed to continuous self-improvement and achieving optimal solutions.

\section*{Work Experience}
\subsection*{Software Engineer, National Energy Commission of Chile, December 2018 - to date}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Led cross-functional teams to improve "Energía Región" ETL scripts in Python.
  \item Played a pivotal role in enhancing the "Energy Sector Daily Report" application as a developer.
  \item Acted as a team leader for the Electric Market Monitoring Platform.
  \item Developed and deployed several processes for the new online procedures platform.
\end{itemize}

\subsection*{Software Engineer, Ministry of Energy of Chile, September 2016 - November 2018}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Successfully designed and managed the development of the new version of the Energy Management platform using C# and ASP.NET as part of the Efficient Government initiative.
  \item Led and developed major changes to the online procedures platform to make it user-friendly for the Citizen Information, Complaints, and Suggestions Office. These enhancements were implemented from version 1 to the current version 2, which is utilized across all government online procedures platforms.
\end{itemize}

\subsection*{Co-Founder and CTO, Synacore SpA, October 2013 - September 2015}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Designed and spearheaded the development of software solutions for company projects, including a joint venture with an Italian partner to enter the Chilean market.
\end{itemize}

\subsection*{Software Quality Assurance Engineer, ALMA Observatory, November 2010 - December 2013}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Led code reviews and ensured the delivery of high-quality software to the observatory.
  \item Led the preparation of three sub-departments for internal quality audits, adhering to ISO 9001:2005 standards.
  \item Successfully managed the audit process and led the resolution of all identified issues, collaborating closely with department heads and managers of each sub-department.
  \item Produced fault analysis reports to track observation downtime due to software or hardware issues.
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Universidad Adolfo Ibáñez, Santiago - Master Degree on Technological Management and Entrepreneurship. In progress.
  \item Babson College, Boston, MA - Babson Build Program, summer 2023.
  \item Universidad Tecnológica Metropolitana, Santiago - Major in Computer Science 2017.
  \item Universidad Tecnológica Metropolitana, Santiago - Bachelor in Engineering Science 2009.
\end{itemize}

\section*{Labor Skills}
\subsection*{Languages}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Spanish (native).
  \item English (advanced level).
  \item German (beginner level).
\end{itemize}

\subsection*{Computer Skills}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Programming languages: C/C++, Java, PHP, C#, Python, Fortran.
  \item Data bases: MySQL, PostgreSQL, SQL Server.
  \item Operating Systems: Linux (Debian, RedHat, CentOS, Ubuntu, Arch, Gentoo), Mac OS X, Windows, FreeBSD.
  \item Others: Shell scripting, R, data mining, machine learning, computer vision.
\end{itemize}

\section*{Other Relevant Experience}
\subsection*{Lecture Assistant, Universidad Tecnológica Metropolitana}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Organize auxiliary lectures for the Programming subject in the Computer Science Major and design the practical assignments for the students.
\end{itemize}

\subsection*{Research assistant, Universidad Tecnológica Metropolitana}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item To configure and keep Linux servers for a high-performance cluster used for scientific computing.
  \item To design and run the research projects in the Environmental Research Laboratory in the Physics Department in Universidad Tecnológica Metropolitana.
\end{itemize}

\section*{Other Relevant Courses}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item Lingoda - German A1 course - 2020.
  \item Instituto Chileno Británico - English Regular courses for adults - 2018.
  \item Udemy - Programming in C# with Visual Studio 2017 - 2018.
  \item Udemy - Creating systems with C# and Asp .netCore Framework - 2017.
  \item SofO2, Santiago - Software Testing Essentials - 2012.
  \item TÜV Rheinland, Santiago - Quality Management System Lead Auditor ISO 9001:2005 - 2011.
  \item Universidad Austral de Chile - English for global purposes - 2010.
\end{itemize}

\section*{Other Interests}
\begin{itemize}[leftmargin=*,itemsep=0pt]
  \item I play the bass guitar in a local rock band and have composed some of the songs for the first studio album.
  \item I enjoy studying all aspects related to music, rhythm, theory, singing, and music technology.
\end{itemize}

\end{document}
